First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
remove abbreviations from abstract

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
Radial Time Projection Chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries (BSA) are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the chiral even Generalized 
Parton Distribution (GPD) $H_{A}$ of $^4$He. This pioneering measurement leads 
the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

>>>>

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer. A new 
Radial Time Projection Chamber was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the chiral even Generalized 
Parton Distribution $H_{A}$ of $^4$He. This pioneering measurement leads 
the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}
